---
title: "Other-Directed Emotion Regulation and Sensitivity to Fairness"
output:
  html_document:
    code_folding: show
    toc: true
    toc_float: true
    toc_depth: 2
    css: !expr here::here("/Users/tur61139/Library/CloudStorage/OneDrive-TempleUniversity/NLP_2026/Kos_RData/StylesTemplates/mk_pro.css")
---

```{r setup, include=F}
# Load libs
library(xfun)
pkg_attach("tidyverse", "Hmisc", "psych", "tibble", "dplyr", "tidyr", "ggplot2", "ggeffects", "sjPlot", "lme4", "car", "emmeans", "scales", "purrr","GGally", "stargazer", "broom", "lmtest", "sandwich", "ggpubr", "performance", "broom.mixed", "gt", "lmerTest", "DataCombine", "MuMIn", "gtsummary", "ggrepel", "corrplot", "writexl", "forcats", "RColorBrewer", "lubridate", "colorBlindness", "interactions", install = TRUE)
options(scipen=999)
options(digits=2)
```

# Loading data
Loading in the .csv files with participant demographic, behavioral (e.g., EROS scores), and neuroimaging data (e.g., extracted cluster values). If you are interested in the data, please email. 
```{r}
# Load .csvs with subject data 
full_df <- read_csv("/Users/tur61139/Documents/GitHub/rf1-kos/df_MRdata_n138.csv")
df <- read_csv("/Users/tur61139/Documents/GitHub/rf1-kos/df_MRcovar_n138.csv")
neural_df <- read_csv("/Users/tur61139/Documents/GitHub/rf1-norms-hpc/n138_filterfunc.csv")
df_extracted <- read_csv("/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/compiled_clusters_n138.csv")
full_df <- left_join(full_df, df, by = "sub_id")
full_df <- full_df |>
  rename(avg_ext_bet = avg_ext_bet.x,
         avg_ext_wor = avg_ext_wor.x,
         avg_int_bet = avg_int_bet.x,
         avg_int_wor = avg_int_wor.x,
         reldep = reldep.x,
         gender_female = gender_female.x,
         gender_male = gender_male.x)

# Trial-level behavioral accept/reject variables 
full_df <- full_df |>
  mutate(offer = R_Option + L_Option, 
         beh_fairness = offer / Endowment,
         accept = ifelse(accept_reject == "Accept", 1, 0),
         
         # Percentage label for plotting
         beh_fairness_perc = case_when(beh_fairness >= 0.060 & beh_fairness <= 0.0625 ~ "5%",
                                       beh_fairness >= 0.09375 & beh_fairness <= 0.125 ~ "10%",
                                       abs(beh_fairness - 0.25) < 1e-6 ~ "25%",
                                       abs(beh_fairness - 0.50) < 1e-6 ~ "50%",
                                       TRUE ~ NA_character_),
         # Numeric binned version for modeling (since )
         beh_fairness_num = case_when(beh_fairness_perc == "5%" ~ 0.05,
                                      beh_fairness_perc == "10%" ~ 0.10,
                                      beh_fairness_perc == "25%" ~ 0.25,
                                      beh_fairness_perc == "50%" ~ 0.50,
                                      TRUE ~ NA_real_),
         # Factor version for plotting
         beh_fairness_perc = factor(beh_fairness_perc, levels = c("5%", "10%", "25%", "50%")))

```

# Sensitivity to fairness calculation
Calculating the 4 different slopes for sensitivities to fairness based on the behavioral data: all-trial, social trials only, nonsocial trials only, then the difference scored social - nonsocial. 
```{r}
## Sensitivity to fairness
# Function to extract subject-level fairness slope
get_fairness_slope <- function(df, label) {
  # Fixed effect of behavioral fairness, random effect with subject
  model <- glmer(accept ~ beh_fairness + (1 + beh_fairness | sub_id), data = df, family = binomial,
    control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
  fe <- fixef(model)[["beh_fairness"]]
  re <- ranef(model)$sub_id[, "beh_fairness"]
  subjIDs <- as.numeric(rownames(ranef(model)$sub_id))
  slopes <- fe + re

  tibble(sub_id = subjIDs, !!label := slopes)
}

# Estimate fairness slopes across all trials, social trials, and nonsocial trials
slope_all_df <- get_fairness_slope(full_df, "slope_all")
slope_social_df <- get_fairness_slope(filter(full_df, condition == "social"), "slope_social")
slope_nonsocial_df <- get_fairness_slope(filter(full_df, condition == "nonsocial"), "slope_nonsocial")

# Merge slopes into one df and compute social - nonsocial difference score
slope_df_wide <- reduce(list(slope_all_df, slope_social_df, slope_nonsocial_df), full_join, by = "sub_id") |>
  mutate(diff_slope = slope_social - slope_nonsocial)
# Printing first 15 subs
print(head(slope_df_wide, 15), digits=3)

# Add slope variables back into the trial-level dataframe
full_df <- left_join(full_df, slope_df_wide, by = "sub_id")
```

# Dataframe for analyses...
```{r}
# Change the names so that it's more legible for figures
pretty_names <- c(gender_female = "Female", gender_male = "Male", sub_age = "Age", sub_gender = "Gender",
                  usi_total = "USI Score", ADI_NATRANK = "ADI (National Rank)", reldep = "Relative Deprivation (z)", 
                  avg_ext_bet.x = "Extrinsic Improving",
                  avg_ext_wor.x = "Extrinsic Worsening",
                  avg_int_bet.x = "Intrinsic Improving",
                  avg_int_wor.x = "Intrinsic Worsening",
                  slope_all = "Sensitivity to Fairness",
                  diff_slope = "Sensitivity to Fairness, S-NS",
                  slope_social = "Social Sensitivity to Fairness",
                  slope_nonsocial = "Nonsocial Sensitivity to Fairness")

# Subject-level covariates pulled from full_df
subject_vars <- full_df |>
  select(sub_id, starts_with("avg_"), ends_with("_MC")) |>
  distinct()

# Add subject-level covariates to df used for downstream analyses
df <- left_join(df, subject_vars, by = "sub_id")

# Long-format slope dataframe for social vs. nonsocial plots
slope_df <- slope_df_wide |>
  left_join(full_df |>
              select(sub_id, avg_ext_bet, avg_ext_wor, avg_int_bet, avg_int_wor, reldep) |>
              distinct(), by = "sub_id") |>
  pivot_longer(cols = c(slope_social, slope_nonsocial), names_to = "condition", values_to = "slope") |>
  mutate(condition = ifelse(condition == "slope_social", "social", "nonsocial"))

# Subject-level acceptance rates within each condition
accept_rates <- full_df |>
  group_by(sub_id, condition) |>
  summarise(accept_rate = mean(accept, na.rm = TRUE), .groups = "drop") |>
  left_join(full_df |>
              select(sub_id, avg_ext_bet, avg_ext_wor, avg_int_bet, avg_int_wor, reldep) |>
              distinct(), by = "sub_id")

# Final df for modeling
df <- left_join(df_extracted, df, by = "sub_id")

# Create df with subject demographic and questionnaire information from long-format trial df
demog_df <- full_df |>
  group_by(sub_id) |>
  slice(1) |>
  ungroup() |>
  select(sub_id, gender_female ,gender_male, sub_age, race, ethnicity, sub_gender,
         usi_total, ADI_NATRANK, reldep, # USI and ADI and relative deprivation 
         avg_ext_bet, avg_ext_wor, avg_int_bet, avg_int_wor, # EROS scores
         slope_all, diff_slope, slope_social, slope_nonsocial)
```

# Behavioral Analyses
## Acceptance Rate
Looking at the acceptance rate for offers across the 4 levels of fairness. In particular, want to see if there is a significant difference in 1) fairness on offer acceptance and 2) fairness and social context (human vs. computer partner) on offer acceptance.
```{r, fig.height=5, fig.width=8}
fairness <- glmer(accept ~ beh_fairness_perc + (1 | sub_id), data = full_df, family = binomial)
summary(fairness)
car::Anova(fairness, type = 3)

fairness_condition <- glmer(accept ~ beh_fairness_perc * condition + (1 | sub_id), data = full_df, family = binomial)
summary(fairness_condition)
car::Anova(fairness_condition, type = 3)


# Summarise with SE and put "social" first
plot_df <- full_df |>
  group_by(beh_fairness_perc, condition) |>
  summarise(n = dplyr::n(),
            accept_rate = mean(accept_binary, na.rm = TRUE),
            sd_accept = sd(accept_binary, na.rm = TRUE),
            se_accept = sd_accept / sqrt(n), .groups = "drop") |>
  mutate(condition = factor(condition, levels = c("social", "nonsocial")),
         ymin = pmax(0, accept_rate - se_accept),
         ymax = pmin(1, accept_rate + se_accept))

pd <- position_dodge(width = 0.8)  # shared dodge object

ggplot(plot_df, aes(x = beh_fairness_perc, y = accept_rate, fill = condition)) +
  geom_hline(yintercept = c(0.25, 0.50, 0.75, 1.00),
           linetype = "solid",
           color = "lightgray",
           linewidth = 0.6) +
  geom_col(width = 0.7, color = "white", position = pd) +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.15, position = pd, linewidth = 0.5) +
  scale_y_continuous(name = "Acceptance Rate", 
                     breaks = c(0, 0.25, 0.50, 0.75, 1.00),
                     labels = scales::label_percent(accuracy = 1)) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_x_discrete(name = "Offer Fairness (% of endowment)") +
  scale_fill_manual(values = c("social" = "#FBB03B", "nonsocial" = "#50C9F1"), breaks = c("social", "nonsocial")) +
  theme_minimal(base_size = 24) +
  theme(panel.grid = element_blank(), axis.title = element_text(size = 15), axis.text = element_text(size = 12), legend.title = element_blank()) 

```
Significant for offer fairness, but not the interaction term. 

## Anterior Insula Categorical Plot
Using data from the categorical model in FSL (level 1 = 5% offer, and so on) to demonstrate the anterior insula tracking offer fairness regardless of a low or high endowment amount. 
```{r fig.height=5, fig.width=8}
# 8 conditions
conditions <- c("/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/thr_seed-AIns.nii.gz_model-3b_type-act_cope-01_cname-nonsocial_level1",
  "/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/thr_seed-AIns.nii.gz_model-3b_type-act_cope-02_cname-nonsocial_level2",
  "/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/thr_seed-AIns.nii.gz_model-3b_type-act_cope-03_cname-nonsocial_level3",
  "/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/thr_seed-AIns.nii.gz_model-3b_type-act_cope-04_cname-nonsocial_level4",
  "/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/thr_seed-AIns.nii.gz_model-3b_type-act_cope-05_cname-social_level1",
  "/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/thr_seed-AIns.nii.gz_model-3b_type-act_cope-06_cname-social_level2",
  "/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/thr_seed-AIns.nii.gz_model-3b_type-act_cope-07_cname-social_level3",
  "/Users/tur61139/Documents/GitHub/rf1-norms/derivatives/imaging_plots/thr_seed-AIns.nii.gz_model-3b_type-act_cope-08_cname-social_level4")

# Weighted means and SEM function thx chat
summarise_condition <- function(cond) {
  val_file <- paste0(cond, ".txt")
  var_file <- file.path(dirname(cond), paste0("var_", basename(cond), ".txt"))
  vals <- scan(val_file, what = numeric(), quiet = TRUE)
  vars <- scan(var_file, what = numeric(), quiet = TRUE)
  if (length(vals) != length(vars)) stop("Lengths differ for ", cond)
  w <- 1 / vars
  tibble(
    condition = basename(cond),
    mean = sum(w * vals) / sum(w),
    sem  = sqrt(1 / sum(w)),
    n    = length(vals))
}

# Weighted means and SEMs
summary_df <- map_dfr(conditions, summarise_condition)

# Parse social and level
cat_plot_df <- summary_df |>
  mutate(social = if_else(str_detect(condition, "nonsocial"), "Nonsocial", "Social"),
    level_digit = str_match(condition, "level(\\d)")[,2],
    level = factor(level_digit, 
                   levels = c("1","2","3","4"),
                   labels = c("5%","10%","25%","50%")),
    cope_num = as.integer(str_match(condition, "cope-(\\d+)")[,2]))

# Plot
ggplot(cat_plot_df, aes(x = level, y = mean, fill = social)) +
  geom_hline(yintercept = c(-15, -10, -5, 0, 5),
           linetype = "solid",
           color = "lightgray",
           linewidth = 0.6) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(aes(ymin = mean - sem, 
                    ymax = mean + sem),
                position = position_dodge(width = 0.8), width = 0.2, linewidth=0.6) +
  scale_fill_manual(values = c("Social" = "#FBB03B", "Nonsocial" = "#50C9F1")) +
  labs(x = "Offer Level (% of endowment)",
       y = "AIns activation (inverse-variance weighted mean)",
       title = "Anterior Insula – Social vs Nonsocial") +
  theme_classic(base_size = 13)

# Subject level df for stats
cat_stats_df <- map_dfr(conditions, function(cond) {
  val_file <- paste0(cond, ".txt")
  vals <- scan(val_file, what = numeric(), quiet = TRUE)
  tibble(sub = factor(seq_along(vals)), condition = basename(cond), value = vals)}) |>
  mutate(social = if_else(str_detect(condition, "nonsocial"), "Nonsocial", "Social"),
         level_digit = str_match(condition, "level(\\d)")[, 2],
         level = factor(level_digit, levels = c("1", "2", "3", "4"),
                        labels = c("5%", "10%", "25%", "50%")))

# Mixed model for fairness level, sociality, and interaction
m_cat <- lmer(value ~ social * level + (1 | sub), data = cat_stats_df)
anova(m_cat)
summary(m_cat)

```

# Activation
## dlPFC, S > NS behavioral sensitivity, Extrinsic Affect Improving (Other-Directed Affect Improving)
```{r fig.height=8, fig.width=10}
# Create High/Low grouping by median split
df$ext_bet_group <- ifelse(subject_vars$avg_ext_bet_MC.x >= median(subject_vars$avg_ext_bet_MC.x, na.rm = TRUE),
                           "High", "Low")

# Get the full 12-color color-blind friendly palette
cb_palette <- SteppedSequential5Steps

# Choose colors
cb_pair <- cb_palette[c(3, 11)]
names(cb_pair) <- c("Low", "High")


# Regression scatterplot with colorblind-safe palette and residualized X and Y
ggplot(df, aes(
  x = diff_slope,
  y = residuals(lm(`act_AlphaDiff-ExtBet-Int_C12_zstat3_cluster1` ~ sub_age_MC + gender_female + gender_male + avg_fdmean_MC + avg_tsnr_MC)),
  color = ext_bet_group,
  fill = ext_bet_group)) +
  geom_point(alpha = 0.5, size = 3) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.2) +
  scale_color_manual(values = cb_pair) +
  scale_fill_manual(values = cb_pair) +
  labs(
    x = "Behavioral Sensitivity to Fairness, \nSocial > Nonsocial (MC)",
    y = "Neural Sensitivity to Fairness, \nSocial > Nonsocial (Residualized)",
    color = "Extrinsic Affect-Improving",
    fill = "Extrinsic Affect-Improving") +
  theme_minimal(base_size = 18) + 
  theme(legend.position="bottom")


# Johnson-Neyman plot version
m_jn <- lm(`act_AlphaDiff-ExtBet-Int_C12_zstat3_cluster1` ~ diff_slope * avg_ext_bet.x +  sub_age_MC + gender_female + gender_male + avg_fdmean_MC + avg_tsnr_MC,
  data = df)

# Obs range of moderator
mf <- model.frame(m_jn)
mod_rng <- range(mf$avg_ext_bet.x, na.rm = TRUE)

# Johnson–Neyman analysis
jn <- johnson_neyman(m_jn,
  pred = "diff_slope",
  modx = "avg_ext_bet.x",
  alpha = 0.05,
  mod.range = mod_rng, 
  sig.color = cb_palette[11],
  insig.color = "gray",
  line.thickness = 1,
  y.label = "Slope of Sensitivity to Fairness, Social > Nonsocial",
  modx.label = "Extrinsic Affect-Improving", 
  title = "Activation, dlPFC, Extrinsic Affect-Improving")
jn
```

# PPI 
## Amygdala, S > NS behavioral sensitivity
```{r fig.height=8, fig.width=10}
diff_amyg <- lm(`amyg_AlphaDiff_C12` ~ sub_age_MC + gender_female + gender_male + avg_fdmean_MC + avg_tsnr_MC, data = df)
# NO BEHAV COVAR OF INTEREST
summary(diff_amyg)

diff_beh <- lm(diff_slope ~ sub_age_MC + gender_female + gender_male + avg_fdmean_MC + avg_tsnr_MC, data = df)
# BEHAV COVAR OF INTEREST AS DV 
summary(diff_beh)

ggplot(df, aes(x = diff_slope, y = `amyg_AlphaDiff_C12`)) +
  geom_smooth(method = "lm", formula = y ~ x,
    se = TRUE, color = "#85CAC7", fill = "#85CAC7", size = 2, alpha = 0.25) +
    geom_point(color = "black", size = 1.5, alpha = 0.8) +
  labs(x = "Behavioral Sensitivity to Fairness",
       y = "Neural Sensitivity to Fairness, S > NS\namygdala–OFC connectivity") +
  theme_minimal() + 
  theme(legend.position="top")

```

## Amygdala-dmPFC, S > NS behavioral sensitivity, Extrinsic Worsening (Other-Directed Affect Worsening)
```{r fig.height=8, fig.width=10}
# amygdala
model_amyg <- lm(`amyg_AlphaDiffExtWor_C12` ~ sub_age_MC + gender_female + gender_male + avg_fdmean_MC + avg_tsnr_MC + diff_slope + avg_ext_wor.x + (diff_slope*avg_ext_wor.x), data=df)
summary(model_amyg)

# Create High/Low grouping by median split
df$extwor_group <- ifelse(df$avg_ext_wor.x >= median(df$avg_ext_wor.x, na.rm = TRUE), "High", "Low")

cbextwor_pair <- SteppedSequential5Steps[c(2, 9)]
names(cbextwor_pair) <- c("High", "Low")

# Regression scatterplot with colorblind-safe palette and residualized Y axis 
ggplot(df, aes(x = diff_slope,
               y = residuals(lm(`amyg_AlphaDiffExtWor_C12` ~ sub_age_MC + gender_female + gender_male + avg_fdmean_MC + avg_tsnr_MC)),
               color = extwor_group, 
               fill = extwor_group)) + 
  geom_point(alpha = 0.5, size = 3) +
  geom_smooth(method = "lm", se = TRUE, alpha = 0.2) +
  scale_color_manual(values = cbextwor_pair) +
  scale_fill_manual(values = cbextwor_pair) +
  labs(x = "Behavioral Sensitivity to Fairness, \nSocial > Nonsocial",
       y = "Neural Sensitivity to Fairness, \nSocial > Nonsocial (Residualized)",
       color = "Extrinsic Affect-Worsening") +
  theme_minimal(base_size = 18) +
  guides(fill = "none", shape = "none") + 
  theme(legend.position="bottom")


# Johnson-Neyman plot version
m_jn <- lm(`amyg_AlphaDiffExtWor_C12` ~ diff_slope * avg_ext_wor.x +  sub_age_MC + gender_female + gender_male + avg_fdmean_MC+ avg_tsnr_MC, data = df)

# Obs range of moderator
mf <- model.frame(m_jn)
mod_rng <- range(mf$avg_ext_wor.x, na.rm = TRUE)

# Johnson–Neyman analysis
jn <- johnson_neyman(m_jn,
  pred = "diff_slope",
  modx = "avg_ext_wor.x",
  alpha = 0.05,
  mod.range = mod_rng, 
  sig.color = cb_palette[1], 
  insig.color = "gray",
  line.thickness = 1,
  y.label = "Slope of Sensitivity to Fairness, Social > Nonsocial",
  modx.label = "Extrinsic Affect-Worsening", 
  title = "PPI, amygdala - vmPFC/OFC , Extrinsic Affect-Worsening")
jn

```

# Behavioral Plots (supplement)
```{r fig.height=8, fig.width=10}
ext_wor_all <- summary(lm(slope_all ~ avg_ext_wor.x, df))
ext_wor_all
ext_bet_all <- summary(lm(slope_all ~ avg_ext_bet.x, df))
ext_bet_all
int_wor_all <- summary(lm(slope_all ~ avg_int_wor.x, df))
int_wor_all
int_bet_all <- summary(lm(slope_all ~ avg_int_bet.x, df))
int_bet_all

ext_wor_soc <- summary(lm(slope_social ~ avg_ext_wor.x, df))
ext_wor_soc
ext_bet_soc <- summary(lm(slope_social ~ avg_ext_bet.x, df))
ext_bet_soc
int_wor_soc <- summary(lm(slope_social ~ avg_int_wor.x, df))
int_wor_soc
int_bet_soc <- summary(lm(slope_social ~ avg_int_bet.x, df))
int_bet_soc

ext_wor_ns <- summary(lm(slope_nonsocial ~ avg_ext_wor.x, df))
ext_wor_ns
ext_bet_ns <- summary(lm(slope_nonsocial ~ avg_ext_bet.x, df))
ext_bet_ns
int_wor_ns <- summary(lm(slope_nonsocial ~ avg_int_wor.x, df))
int_wor_ns
int_bet_ns <- summary(lm(slope_nonsocial ~ avg_int_bet.x, df))
int_bet_ns

# Difference between social and nonsocial context, extrinsic worsening trait in behavior (no difference in context)
df_long_beh <- data.frame(slope = c(df$slope_social, df$slope_nonsocial),
  eros  = c(df$avg_ext_wor.x, df$avg_ext_wor.x),
  context = factor(rep(c("social", "nonsocial"), each = nrow(df))))

model_contextdiff <- lm(slope ~ eros * context, df_long_beh)
summary(model_contextdiff)

vars <- c("avg_ext_bet.x", "avg_ext_wor.x","avg_int_bet.x", "avg_int_wor.x")

for (v in vars) {
  p <- ggplot(df, aes(x = slope_all, y = .data[[v]])) +
    geom_point(alpha = 0.6) +
    geom_smooth(method = "lm", se = TRUE) +
    theme_minimal() +
    labs(title = paste(v, "Behavioral Sensitivity to Fairness"),
      x = "Sensitivity to Fairness",
      y = v)
    print(p)}

df_long <- df |>
  select(slope_all, avg_ext_bet.x, avg_ext_wor.x, avg_int_bet.x, avg_int_wor.x) |>
  pivot_longer(-slope_all, names_to = "EROS_scale", values_to = "score")

df_long$EROS_scale <- factor(df_long$EROS_scale,
  levels = c("avg_ext_bet.x", "avg_ext_wor.x", "avg_int_bet.x", "avg_int_wor.x"),
  labels = c("Extrinsic Improving", "Extrinsic Worsening", "Intrinsic Improving", "Intrinsic Worsening"))

ggplot(df_long, aes(x = slope_all, y = score)) +
  geom_smooth(aes(color = EROS_scale, fill = EROS_scale), method = "lm", se = TRUE, linewidth = 1.2, alpha = 0.2) +
  geom_point(color = "black", alpha = 0.8) + 
  facet_wrap(~ EROS_scale) +
  scale_color_manual(values = c("Extrinsic Improving" = "green3",
                                "Extrinsic Worsening" = "red2",
                                "Intrinsic Improving" = "goldenrod2",
                                "Intrinsic Worsening" = "blue2")) +
  scale_fill_manual(values = c("Extrinsic Improving" = "green3",
                               "Extrinsic Worsening" = "red2",
                               "Intrinsic Improving" = "goldenrod2",
                               "Intrinsic Worsening" = "blue2")) +
  guides(color = "none", fill = "none") +
  labs(x = "Sensitivity to Fairness",
       y = "EROS Subscale Score", 
       caption = "Shaded regions represent 1 standard error of the estimated regression line.") +
  theme_minimal(base_size = 16)

```

